\vspace{-5pt}
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading{Infosys Limited - Loreal USA}{Hybrid}
    {Data Engineer (Full-time)}{Feb 2020 - July 2022}
    \resumeItemListStart
        \resumeItem{Responsibilities}
          {To enable multigrain insights on e-retail sales and ads running on amazon portal}
        \resumeItem{Technologies and frameworks}
          {Google Cloud Platform, Python and SQL}
        \resumeItem{Goals Achieved}
          {\begin{itemize}
              \item Built High scalable 4 layer architecture(raw, curated, semantic \& Consumption) to handle huge workloads effectively
              \item Developed and maintained data pipelines and analytics solutions on GCP.
              \item Created data models and implement automated data validation checks to ensure data quality.
              \item Worked with SQL and NoSQL databases to query and analyze data.
              \item Achieved metadata driven composer(Airflow) data pipelines to orchestrate data pipelines to perform ETL operations.
              \item Created automated scripts controlled by GCP cloud functions to monitor daily file loading improving efficiency and reducing processing time by 60\%
              \item Worked with business stakeholders to identify and understand data requirements, and created data models to support business needs.
          \end{itemize}}
      \resumeItemListEnd
    \vspace{-5pt}
    \resumeSubheading{Glean Solutions}{Remote}
    {Firmware Developer (Freelancer)}{Nov 2018 - Jan 2020}
    \resumeItemListStart
        \resumeItem{Responsibilities}
          {Building of smart home automation devices based on data from real-time sensors and user controlling}
        \resumeItem{Technologies and frameworks}
          {Raspibian, Home Assistant, Embedded C, Arduino, Python and SQL}
        \resumeItem{Goals Achieved}
          {\begin{itemize}
              \item Designed, developed, and maintained firmware for home automation devices, including smart locks, thermostats, and security systems.
              \item Worked with wireless communication protocols such as Wi-Fi, Zigbee, and Bluetooth, to ensure seamless connectivity between devices and mobile applications.
              \item Implemented firmware updates and bug fixes, and conducted thorough testing and validation to ensure high quality and reliability of the firmware.
              \item Worked with hardware engineers to develop custom PCBs for smart lighting systems, optimizing performance and reducing costs.
              \item Designed and developed firmware for smart home lighting systems, including drivers for various lighting components and integration with voice assistants such as Amazon Alexa and Google Home.
          \end{itemize}}
      \resumeItemListEnd
    \vspace{-5pt}
    \vspace{-5pt}

  \resumeSubHeadingListEnd
