\vspace{-5pt}
\setlength{\footskip}{3.60004pt}
\section{Projects}
\resumeSubHeadingListStart
\resumeSubItem{CNN based body rash prediction application with AR technology}{(Work in progress) Research oriented, open source Body rash prediction application to detect and predict type of rash upon scanning the image. It gives us high level analysis and suggests necessary precautions to take before consulting a medical practitioner which saves 50\% time and money.
Tech: Python, opencv,TensorFlow,keras.}
\vspace{2pt}
\resumeSubItem{Cloud based Serverless ETl architecture}{(Work in progress) Severless model gives us high flexibility in scaling and maintaining workload by reducing 60\% overall cost for an ETL/ELT data pipelines. With this opensource architecture, one can deploy on any cloud with their respective services with ease and comfort.
Tech: Python, GCP cloud, AWS cloud, DBT, FLASK, docker}
\vspace{2pt}
\resumeSubItem{Raspberry controlled Home automation}{ Retrofitted smart devices enables you to monitor and control your home appliances from anywhere in the world. With this technology, we can reduce 40\% of the energy consumption and configure daily routines according to our lifestyle to make life easy.
Tech: Embedded Python, Embedded C, sensor networks,pubsub, I2C communication, Networking (September '18)}
\vspace{2pt}
\resumeSubItem{Amphibot- An underwater surveillance robot with object detection}{Amphibot is a smart amphibian robot powered with high end computing system to detect objects and collect samples. This AI based robot can be used at the places where humans are not able to reach. Tech: Raspberry, Arduino, Python, Embedded C, tensorflow, opencv, BLE, sensor network}
\resumeSubHeadingListEnd
\vspace{-5pt}
